Single-step Hybrid Predition

### 2017-01-31 reports/data_overview.Rmd
Save names of reduced set of 685 hybrids

red_hybrid <- full_hybrid %>%
  as_data_frame() %>%
  separate(value, into = c("DF", "Dent", "Flint")) %>%
  mutate(Avail_Dent = ifelse(Dent %in% red_inbreds$Dent, yes = 1, no = 0),
         Avail_Flint = ifelse(Flint %in% red_inbreds$Flint, yes = 1, no = 0),
         Tested_Parents = Avail_Dent + Avail_Flint) %>%
  filter(Tested_Parents == 2) %>%
  unite(Hybrid, DF, Dent, Flint) %>%
  .$Hybrid
genos <- genos %>%
  rbind(tibble(G = red_hybrid,
               Pool = "Hybrid",
               Data_Type = "mrna")
        )
```

>>>>

red_hybrid <- full_hybrid %>%
  as_data_frame() %>%
  separate(value, into = c("DF", "Dent", "Flint")) %>%
  mutate(Avail_Dent = ifelse(Dent %in% red_inbreds$Dent, yes = 1, no = 0),
         Avail_Flint = ifelse(Flint %in% red_inbreds$Flint, yes = 1, no = 0),
         Tested_Parents = Avail_Dent + Avail_Flint) %>%
  filter(Tested_Parents == 2) %>%
  unite(Hybrid, DF, Dent, Flint) %>%
  .$Hybrid
saveRDS(red_hybrid, "./data/processed/hybrids_685.RDS")
genos <- genos %>%
  rbind(tibble(G = red_hybrid,
               Pool = "Hybrid",
               Data_Type = "mrna")
        )
```
